Manuscript

### 2017-06-26 manuscript.Rmd
Added geojson files to the manuscript
Added Denver 'results' section and calculated impacts of Denver SDM models.

```{r setup}
library(geojsonio)
library(leaflet)
```

@@

>>>>

```{r setup}
library(geojsonio)
library(leaflet)
library(tidyverse)
library(spdep)
library(maptools)
library(rgdal)
library(rgeos)
library(texreg)
library(leaflet)
```

@@

## Denver

Load Denver geospatial data (tracts and parks):
```{r denver_data}
tracts <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
plot(tracts)

parks <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
plot(parks)
```

Transform the attribute table into a tibble and select the relevant variables:
```{r show_denverdata}
tracts@data <- tbl_df(tracts@data) %>%
  select(GEOID_TRAC, OBESITY, Park_Percent, PhysAct, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegePercent, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
tracts@data
```

Calculate the logsum given a tracts and parks dataset:
```{r denver_accessibility}
source('R/size00001dist5.R', echo=TRUE)
tracts$park_ls <- calculate_park_logsums(tracts, parks, betas = c(.00001, -5))
```

Create regression equations for use in spatial econometric models:
```{r denver_equations}
denver_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)

denver_parks_formula <- update(base_formula, . ~ . + park_ls)
```

Locate the centroid of all parks and all census tracts and create a distance matrix:
```{r denver_distancematrix}
tract_centroids <- gCentroid(tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
park_centroids <- gCentroid(parks, byid = TRUE)
distance_matrix <- gDistance(tract_centroids, park_centroids, byid = TRUE)
dim(distance_matrix)
```

Create a spatial weights matrix:
```{r denver_W}
neighbors <- poly2nb(tracts, queen = FALSE)
W <- nb2listw(neighbours = neighbors, zero.policy = TRUE)
print(W, zero.policy = TRUE)
```

Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
```{r denver_spmodels_obesity}
denver_obese_sem <- errorsarlm(update(denver_base_formula, OBESITY ~ .), data = tracts@data, 
                      listw = W, zero.policy = TRUE)
denver_obese_sem2 <- errorsarlm(update(denver_parks_formula, OBESITY ~ .), data = tracts@data, 
                      listw = W, zero.policy = TRUE)
denver_obese_sdm <- lagsarlm(update(denver_base_formula, OBESITY ~ .), data = tracts@data, 
                      listw = W, zero.policy = TRUE, type = "mixed")
denver_obese_sdm2 <- lagsarlm(update(denver_parks_formula, OBESITY ~ .), data = tracts@data, 
                      listw = W, zero.policy = TRUE, type = "mixed")
```

Estimate spatial econometric models for the `PhysAct` variable. The first model of each different type does not include `park_ls`:
```{r denver_spmodels_physact}
denver_physact_sem <- errorsarlm(update(denver_base_formula, PhysAct ~ .), data = tracts@data, 
                          listw = W, zero.policy = TRUE)
denver_physact_sem2 <- errorsarlm(update(denver_parks_formula, PhysAct ~ .), 
                           data = tracts@data, listw = W, zero.policy = TRUE)
denver_physact_sdm <- lagsarlm(update(denver_base_formula, PhysAct ~ .), data = tracts@data, 
                        listw = W, zero.policy = TRUE, type = "mixed")
denver_physact_sdm2 <- lagsarlm(update(denver_parks_formula, PhysAct ~ .), data = tracts@data,
                         listw = W, zero.policy = TRUE, type = "mixed")
```

Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
```{r denver_spmodels_mental}
denver_mental_sem <- errorsarlm(update(denver_base_formula, MENTAL ~ .), data = tracts@data, 
                          listw = W, zero.policy = TRUE)
denver_mental_sem2 <- errorsarlm(update(denver_parks_formula, MENTAL ~ .), 
                           data = tracts@data, listw = W, zero.policy = TRUE)
denver_mental_sdm <- lagsarlm(update(denver_base_formula, MENTAL ~ .), data = tracts@data, 
                        listw = W, zero.policy = TRUE, type = "mixed")
denver_mental_sdm2 <- lagsarlm(update(denver_parks_formula, MENTAL ~ .), data = tracts@data,
                         listw = W, zero.policy = TRUE, type = "mixed")
```

Calculate the impacts of the spatial durbin models:
```{r denverSDM_impacts}
listw <- as(W, "CsparseMatrix")
tr_mult <- trW(listw, type="mult")
tr_MC <- trW(listw, type="MC")
set.seed(1)

denver_noparks_obesemult <- impacts(denver_obese_sdm, tr=tr_mult)
denver_parks_obesemult <- impacts(denver_obese_sdm2, tr=tr_mult)
denver_noparks_obeseMC <- impacts(denver_obese_sdm, tr=tr_MC)
denver_parks_obeseMC <- impacts(denver_obese_sdm2, tr=tr_MC)

denver_noparks_physactmult <- impacts(denver_physact_sdm, tr=tr_mult)
denver_parks_physactmult <- impacts(denver_physact_sdm2, tr=tr_mult)
denver_noparks_physactMC <- impacts(denver_physact_sdm, tr=tr_MC)
denver_parks_physactMC <- impacts(denver_physact_sdm2, tr=tr_MC)

denver_noparks_mentalmult <- impacts(denver_mental_sdm, tr=tr_mult)
denver_parks_mentalmult <- impacts(denver_mental_sdm2, tr=tr_mult)
denver_noparks_mentalMC <- impacts(denver_mental_sdm, tr=tr_MC)
denver_parks_mentalMC <- impacts(denver_mental_sdm2, tr=tr_MC)
```

Compare the models with `htmlreg()`. First the obesity models:
```{r denver_obesity_summary, results="asis", eval=FALSE}
denver_obesity_models <- list(denver_obese_sem, denver_obese_sem2, denver_obese_sdm, denver_obese_sdm2)
names(denver_obesity_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
```

Next, the physical activity models:
```{r denver_physact_summary, results="asis", eval=FALSE}
denver_physact_models <- list(denver_physact_sem, denver_physact_sem2, denver_physact_sdm, denver_physact_sdm2)
names(denver_physact_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
```

And third, the mental health models:
```{r denver_mental_summary, results="asis", eval=FALSE}
denver_mental_models <- list(denver_mental_sem, denver_mental_sem2, denver_mental_sdm, denver_mental_sdm2)
names(denver_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(denver_physact_models, caption = "Denver: Models of Variation in Self-Reported Mental Health")
```

## Boston
```{r boston_models}

```

```{r bostonSDM_impacts}

```

##New York City
```{r nyc_models}

```

```{r nycSDM_impacts}

```
